### 2016-05-26 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Began writing the summary for the gas burner experiments report

Nine full-scale fire experiments were performed to study how the tactics described above affect ventilation and the fire environment within a structure. The tests were conducted in two structures designed to replicate typical residential dwellings. During each experiment, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents. During a number of the tests, a PPV fan was used in conjunction with the opening and closing of vents to further affect the ventilation conditions within the fire environment. This report contains in-depth descriptions of the setup and procedure used for each of the nine experiments.

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:30		  &	   35:00		&	   55:00	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:45	&	13:15	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\chapter{Summary}
\label{chap:Summary}

>>>>

Nine full-scale fire experiments were performed to study how the tactics described above affect ventilation and the fire environment within a structure. The tests were conducted in two structures designed to replicate typical residential dwellings. During each experiment, propane was provided to three diffusion flame burners. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents. During a number of the tests, a PPV fan was used in conjunction with the opening and closing of vents to further affect the ventilation conditions within the fire environment. This report contains in-depth descriptions of the setup and procedure used for each of the nine experiments.

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:30		  &	   35:00		&	   55:00	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:45	&	13:15	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.86\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

@@

\chapter{Summary}
\label{chap:Summary}
Nine full-scale fire tests were conducted in two residential-sized structures to examine how changing ventilation patterns within a structure affects the fire environment. The fire source for each experiment was provided by a set of three diffusion flame burners with propane as the fuel. Various doors and vents were opened and closed during each test to affect the ventilation within the structure. A PPV fan was also used during some of the experiments to change the ventilation patterns. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during each experiment. The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire for each test.
